---
title: "Detecting unit roots"
author: "Jeff Chen"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Testing for a unit root with unitrootML}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

In this vignette, we illustrate how to apply the pre-trained unitrootML unit root test to a set of time series.

## Set up

Set up requires installation from the Github page
```{r, message=FALSE, warning=FALSE}
#Load package
  library(unitrootML)
  library(forecast)
  library(ggplot2)
```

For this example, we will simulate five time series: two with a unit root (`gamma = 1`) and three without a unit root (`gamma < 1`). These time series are stored in a list object. Let's take a look at a few of these time series using `autoplot` from the forecast package and arranged into a grid using `grid.arrange`.

```{r, fig.width = 7, fig.height = 7}
 #Example time series
    set.seed(123)
    out <- list(series1 = ts(dgp_enders1(gamma = 1), freq = 12, start = c(2010,1)),
                series2 = ts(dgp_enders1(gamma = 1), freq = 12, start = c(2010,1)),
                series3 = ts(dgp_enders1(gamma = 0.98), freq = 12, start = c(2010,1)),
                series4 = ts(dgp_enders1(gamma = 0.8), freq = 12, start = c(2010,1)),
                series5 = ts(dgp_enders1(gamma = 0.5), freq = 12, start = c(2010,1)))

  #Plot
    gridExtra::grid.arrange(autoplot(out[[1]]), 
                            autoplot(out[[2]]), 
                            autoplot(out[[3]]), 
                            autoplot(out[[4]]), 
                            autoplot(out[[5]]), 
                            ncol = 2)
```

To screen these time series, apply the `ml_test_all` function, which expects a list object containing time series objects (`bank =`) and a`pvalue = 0.05` to return results evaluated at a 5% level.

```{r}
  res <- ml_test(bank = out, 
                 pvalue = 0.05)
```

The `res` object captures the outputs of a battery of tests, including pre-trained ML-based unit root tests. The first element summarizes the verdict that each unit root test reached when evaluating each time series ("yes" = "unit root"). While each of the traditional tests may disagree, it is worth noting that the tests built on Random Forest (`verdict_ranger`) and Gradient Boosting (`verdict_xgbTree`) offer markedly improved diagnostic accuracy.

```{r}
  verdicts <- res$verdicts
  print(verdicts[,1:5])
```

The test statistics and their critical thresholds are recorded in the `results` element.

```{r}
  results <- res$results
  print(results[,1:5])
```

Lastly, all the input features for the ML-based tests that were calculated from the time series list are available in the `features` element. 

```{r}
  feats <- res$features
  feats[,1:4]
```

For more in-depth background on the construction and properties of the ML-based unit root test, read Cornwall, Chen, and Sauley (2021).
